Trauma treatment delay

### 2023-12-08 manuscriptlongversion.Rmd
text

##

>>>>

In future studies building upon this one, various methods to further
examine the correlation between delayed treatment and various variables,
alternatively using another ofi as the outcome variable. Examining
different variables such as highest hospital care lever, intubation
status or first emergency procedure performed might be interesting
variables, among others. To be able to do this, more patients in the
outcome group would be needed, either by expanding the register to
several hospitals, or expanding the outcome group by adding different
ofi. This however would make the study less specific for delayed
treatment. Further studies might also look into different ofi other than
delayed treatment, such as

## Conclusion

# Abstract
